% Opening Section
\section*{To the Persian People Worldwide}
\addcontentsline{toc}{section}{To the Persian People Worldwide}

\begin{tcolorbox}[colback=persiangold!10!white,colframe=persianblue,width=\textwidth,arc=3mm,boxrule=2pt]

\textbf{\Large Az M\=a Beh M\=a --- From Us, For Us}

\vspace{0.3cm}

To our brothers and sisters of Persian heritage, wherever you may be:

\vspace{0.2cm}

In Los Angeles and London, in Toronto and Tel Aviv, in Sydney and Stockholm, in Dubai and Berlin---millions of us carry the legacy of Persian civilization in our hearts. We are the children of Cyrus, heirs to an empire that stretched from Egypt to India, descendants of poets and scientists, mathematicians and philosophers.

\vspace{0.2cm}

Our ancestor Cyrus the Great showed the world a different way to build an empire---not through terror and subjugation, but through tolerance and respect for human dignity. When he conquered Babylon, he freed the enslaved. When he ruled diverse peoples, he honored their gods and customs. He wrote the first declaration of human rights on a clay cylinder that still inspires the United Nations today.

\vspace{0.2cm}

\textbf{CYRUS token is our digital continuation of this legacy.}

\vspace{0.2cm}

This is not merely a cryptocurrency---it is a symbol of Persian unity, a tool for community empowerment, and a means to preserve and promote our rich cultural heritage for generations to come. Through the CYRUS DAO, we will fund Persian language schools, cultural centers, historical preservation, and humanitarian initiatives that would make our great ancestor proud.

\vspace{0.2cm}

\textit{Zendeh b\=ad Ir\=an. Zendeh b\=ad Kourosh.}

\vspace{0.2cm}

Long live Iran. Long live Cyrus.

\end{tcolorbox}
