\section{The Moment We Are In}

\begin{center}
\textit{``Come, come, whoever you are,\\
Wanderer, worshiper, lover of leaving.\\
It doesn't matter.\\
Ours is not a caravan of despair.''}\\
\vspace{0.2cm}
--- Rumi (Jalal ad-Din Muhammad Balkhi)
\end{center}

\vspace{0.5cm}

\subsection{Iran at the Crossroads}

We stand at a historic inflection point. After more than four decades of theocratic rule, the people of Iran have risen. The \textbf{Woman, Life, Freedom} movement---sparked by the death of Mahsa Jina Amini in September 2022---revealed what the world had forgotten: the Persian spirit cannot be extinguished.

From the streets of Tehran to the mountains of Kurdistan, from Isfahan to Shiraz, Iranians have declared with their blood and their courage: \textit{``We want our country back.''}

\begin{tcolorbox}[colback=persianred!10!white,colframe=persianred,width=\textwidth,arc=3mm,boxrule=2pt]
\centering
\textbf{\Large Zan, Zendegi, Azadi}\\
\vspace{0.2cm}
\textit{Woman, Life, Freedom}\\
\vspace{0.3cm}
This is not merely a slogan---it is the battle cry of a civilization reclaiming its soul.\\
It echoes the same principles Cyrus proclaimed 2,500 years ago:\\
\textbf{Freedom. Dignity. The sanctity of human life.}
\end{tcolorbox}

\subsection{The Diaspora's Sacred Duty}

We, the 8 million Iranians living outside our homeland, carry a profound responsibility. We have what our brothers and sisters inside Iran do not:

\begin{itemize}[leftmargin=*]
    \item \textbf{Freedom of speech} --- We can organize, advocate, and mobilize without fear
    \item \textbf{Financial resources} --- The diaspora controls significant capital
    \item \textbf{Global networks} --- We are embedded in the world's most powerful institutions
    \item \textbf{Technical expertise} --- Iranian engineers and entrepreneurs lead in technology
    \item \textbf{Safety} --- We can take risks our families inside cannot
\end{itemize}

With these advantages comes obligation. We cannot sit idle while our homeland burns. We cannot watch from comfortable distance as young Iranians sacrifice everything for freedom.

\textbf{CYRUS is our answer.} A decentralized treasury, governed by the diaspora, funding the liberation and rebuilding of Iran.

\subsection{Why This Moment Matters}

History teaches us that regimes do not fall on their own. They fall when:

\begin{enumerate}[leftmargin=*]
    \item The people lose fear and rise up --- \textit{Happening now}
    \item The diaspora provides sustained support --- \textit{Our mission}
    \item A credible alternative emerges --- \textit{The Pahlavi path}
    \item International pressure mounts --- \textit{Growing daily}
\end{enumerate}

The Islamic Republic is weaker than it has ever been. Sanctions bite. The economy crumbles. The people have lost faith. The Revolutionary Guard is stretched thin.

\textbf{This is our window. This is our generation's calling.}
