\section{Why Blockchain?}

\subsection{Censorship Resistance for a Censored People}

The Islamic Republic has built one of the world's most sophisticated censorship systems. VPNs are blocked. Social media is filtered. Bank accounts are frozen for political activity. Journalists are imprisoned for tweets.

\textbf{Blockchain breaks these chains.}

\begin{itemize}[leftmargin=*]
    \item \textbf{No central authority can freeze CYRUS} --- Unlike bank accounts
    \item \textbf{No government can censor transactions} --- The blockchain is global
    \item \textbf{No border restricts participation} --- Iranians inside and outside can hold CYRUS
    \item \textbf{Transparent treasury} --- Every rial/dollar accounted for on-chain
    \item \textbf{Democratic governance} --- No single leader controls the funds
\end{itemize}

\subsection{Sanctions Workaround for Humanitarian Aid}

International sanctions---while targeting the regime---have devastated ordinary Iranians. The banking system is cut off. Remittances are nearly impossible. Families are separated from financial support.

Cryptocurrency offers a lifeline:

\begin{itemize}[leftmargin=*]
    \item Diaspora can support families without banking intermediaries
    \item Humanitarian aid can flow directly to those in need
    \item Activists inside Iran can receive support safely
    \item Cultural organizations can receive funding despite restrictions
\end{itemize}

\textbf{Note:} CYRUS is designed for legitimate humanitarian and cultural purposes. We condemn any use that violates applicable laws and will work with legal counsel to ensure compliance.

\subsection{Building the Infrastructure for Free Iran}

When Iran is free---and it \textit{will} be free---it will need modern financial infrastructure. The CYRUS community is building:

\begin{itemize}[leftmargin=*]
    \item Experience in decentralized governance (for future democratic institutions)
    \item Technical expertise in blockchain (for Iran's digital economy)
    \item Global networks of Persian professionals (for reconstruction)
    \item Capital reserves (for rebuilding infrastructure, schools, hospitals)
    \item Transparent treasury management (model for accountable government)
\end{itemize}

We are not just waiting for freedom. We are building the tools and skills that a free Iran will need.
