\section{The Vision: A Free Iran}

\subsection{What We Are Building Toward}

We are not building a cryptocurrency project. We are building the infrastructure for Iranian liberation and reconstruction. When the Islamic Republic falls---and it \textit{will} fall---we will be ready.

\begin{tcolorbox}[colback=persiangold!10!white,colframe=persianblue,width=\textwidth,arc=3mm,boxrule=2pt]
\centering
\textbf{\Large The Iran We Will Build}

\vspace{0.3cm}

\begin{tabular}{ll}
\textbf{Secular} & Religion is personal, government is for all\\
\textbf{Democratic} & Chosen by the people, accountable to the people\\
\textbf{Federal} & Respecting all ethnicities and regions\\
\textbf{Modern} & Leading in technology, science, culture\\
\textbf{Prosperous} & An economy worthy of our human capital\\
\textbf{Free} & The Cyrus Cylinder as our constitution\\
\end{tabular}
\end{tcolorbox}

\subsection{The DAO's Role in Liberation}

The CYRUS DAO treasury will fund direct action for Iranian freedom:

\textbf{Immediate Priorities:}
\begin{itemize}[leftmargin=*]
    \item \textbf{Secure Communications} --- Fund VPN and encryption tools for activists inside Iran
    \item \textbf{Protest Support} --- Legal defense, medical aid, family support for arrested protesters
    \item \textbf{Media Operations} --- Independent Persian journalism, documentary production
    \item \textbf{International Advocacy} --- Lobbying democratic governments for support
    \item \textbf{Activist Networks} --- Connecting cells inside Iran with diaspora resources
\end{itemize}

\textbf{Transition Phase (When the Regime Falls):}
\begin{itemize}[leftmargin=*]
    \item \textbf{Interim Government Support} --- Technical expertise for transition administration
    \item \textbf{Election Infrastructure} --- Transparent voting systems for first free elections
    \item \textbf{Security Sector Reform} --- Training for democratic policing
    \item \textbf{Media Pluralism} --- Funding independent newspapers, TV, radio
    \item \textbf{Civil Society} --- Grants for NGOs, unions, professional associations
\end{itemize}

\textbf{Reconstruction Phase:}
\begin{itemize}[leftmargin=*]
    \item \textbf{Schools} --- Rebuild secular education from primary to university
    \item \textbf{Healthcare} --- Modern hospitals, clinics, medical training
    \item \textbf{Infrastructure} --- Roads, bridges, telecommunications
    \item \textbf{Environment} --- Restore Lake Urmia, forests, air quality
    \item \textbf{Cultural Sites} --- Preserve Persepolis, Pasargadae, Isfahan
    \item \textbf{Repatriation Support} --- Help diaspora families return home
\end{itemize}

\subsection{A Call to Every Persian}

This is bigger than any token, any investment, any individual. This is about:

\begin{center}
\textit{Your grandmother who still dreams of the Iran of her youth.}\\
\textit{Your cousins who cannot speak freely in their own country.}\\
\textit{The young woman who removed her hijab and was beaten for it.}\\
\textit{The student who tweeted and was imprisoned for it.}\\
\textit{The poet whose words are banned from bookstores.}\\
\textit{The 2,500 years of civilization that refuse to be erased.}
\end{center}

Every CYRUS token you hold is a vote for freedom. Every proposal you support is a brick in the foundation of a new Iran. Every Persian you bring into this community strengthens our collective power.

\begin{tcolorbox}[colback=persianred!10!white,colframe=persianred,width=\textwidth,arc=3mm,boxrule=2pt]
\centering
\textbf{\Large M\=a Ham\=e B\=a Ham Hast\=im}\\
\vspace{0.2cm}
\textit{We Are All Together}\\
\vspace{0.3cm}
The regime divides us by ethnicity, by religion, by politics.\\
\textbf{CYRUS unites us by heritage, by values, by destiny.}\\
\vspace{0.2cm}
Persian, Kurd, Azeri, Baluch, Lor, Gilaki, Arab---\\
\textbf{We are all children of Cyrus. We are all Iran.}
\end{tcolorbox}

\newpage
