\section{Conclusion: The Spirit of Cyrus Lives On}

Twenty-five centuries have passed since Cyrus the Great conquered Babylon and proclaimed freedom for the enslaved, dignity for the oppressed, and tolerance for all beliefs. Empires have risen and fallen. The world has transformed beyond recognition. Yet the principles he championed remain as vital as ever.

Today, millions of Persians live scattered across the globe---a diaspora born of upheaval but carrying within it the seeds of a great civilization. We carry the poetry of Rumi and Hafez in our hearts, the mathematics of Khayyam in our minds, and the principles of Cyrus in our souls.

\textbf{But we also carry a burden: the knowledge that our homeland is not free.}

For over forty years, the Iranian people have lived under a regime that betrays everything Cyrus stood for. Where he freed the enslaved, they imprison the innocent. Where he honored all faiths, they impose religious tyranny. Where he celebrated human dignity, they execute dissidents and beat women in the streets.

\textbf{This ends with us.}

The CYRUS token is not just a symbol---it is a tool. A tool for organizing the diaspora. A tool for funding resistance. A tool for building the institutions that a free Iran will need. A tool for turning our collective grief and anger into collective action.

When the historians of the future write the story of Iran's liberation, they will ask: \textit{``Where were you? What did you do?''}

Let our answer be: \textit{``We were there. We organized. We funded. We fought. We won.''}

As it is written at Pasargadae:

\begin{center}
\textit{``O man, whoever you are, from wherever you come,\\
for I know you shall come---\\
I am Cyrus, who founded the Persian Empire.''}
\end{center}

We have come, O Cyrus. We have come from Los Angeles and London, from Toronto and Tel Aviv, from every corner of the world where your children have scattered. We have come with blockchain as our tool and your principles as our guide.

\textbf{And we will not rest until Iran is free.}

\vspace{1cm}

\begin{center}
\rule{0.5\textwidth}{0.4pt}

\vspace{0.5cm}

{\Large\bfseries\color{persianblue} Zendeh B\=ad Kourosh-e Bozorg}

\vspace{0.2cm}

{\large Long Live Cyrus the Great}

\vspace{0.3cm}

{\Large\bfseries\color{persianred} Zendeh B\=ad Ir\=an}

\vspace{0.2cm}

{\large Long Live Iran}

\vspace{0.5cm}

\textbf{\large Zan, Zendegi, \=Az\=adi}

\vspace{0.2cm}

\textit{Woman, Life, Freedom}

\vspace{0.5cm}

{\color{persiangold}$\bigstar$} \textsc{For the PARS Community \& Diaspora} {\color{persiangold}$\bigstar$}

\vspace{0.3cm}

{\color{persiangold}$\bigstar$} \textsc{For a Free Iran} {\color{persiangold}$\bigstar$}

\end{center}

\newpage
