\section{The Path to Universal Liberty}

\begin{center}
\textit{``The wound is the place where the Light enters you.''}\\
\vspace{0.2cm}
--- Rumi
\end{center}

\vspace{0.5cm}

The struggle for Iranian freedom is part of a larger story---the story of humanity's long march toward liberty. From the Cyrus Cylinder to the Magna Carta, from the Declaration of the Rights of Man to the Universal Declaration of Human Rights, from Gandhi's salt march to Mandela's long walk to freedom---we stand in a tradition of those who dared to imagine a world where every person lives in dignity.

\subsection{Freedom as a Universal Principle}

Cyrus the Great did not liberate only Persians. He freed Babylonians, Jews, Elamites, Medes---every people under his rule. His principle was universal: \textit{all human beings deserve freedom and dignity, regardless of their origin, faith, or station.}

This universalism is our inheritance and our obligation.

\begin{tcolorbox}[colback=persianblue!10!white,colframe=persianblue,width=\textwidth,arc=3mm,boxrule=2pt]
\centering
\textbf{\Large The CYRUS Principles of Universal Liberty}

\vspace{0.3cm}

\begin{enumerate}[leftmargin=*]
    \item \textbf{Dignity is inherent}: Every human being possesses inviolable dignity by virtue of being human
    \item \textbf{Freedom is indivisible}: No one is truly free until all are free
    \item \textbf{Power must be accountable}: Authority derives from consent and serves the governed
    \item \textbf{Truth must be spoken}: Transparency and honest witness are moral imperatives
    \item \textbf{Mercy transcends vengeance}: Justice seeks healing, not destruction
    \item \textbf{The future belongs to builders}: Those who create outcompete those who destroy
\end{enumerate}
\end{tcolorbox}

\subsection{The Tools of Liberation}

Every liberation movement requires tools. Ours include:

\begin{itemize}[leftmargin=*]
    \item \textbf{Economic coordination}: The CYRUS token and DAO treasury
    \item \textbf{Transparent governance}: On-chain voting and constitutional constraints
    \item \textbf{Cultural preservation}: Funding for language, art, heritage
    \item \textbf{Humanitarian action}: Direct support for those in need
    \item \textbf{Secure communications}: Cryptographic protocols that cannot be surveilled
    \item \textbf{Truth documentation}: Journalism, human rights records, historical archives
\end{itemize}

The following section specifies a communications protocol that ensures activists, journalists, and ordinary citizens can coordinate without fear of interception.
