\section{A Call to Artists, Mathematicians, and Cryptographers}

\begin{center}
\textit{``Sell your cleverness and buy bewilderment.\\
Cleverness is mere opinion, bewilderment is intuition.''}\\
\vspace{0.2cm}
--- Rumi
\end{center}

\vspace{0.5cm}

The liberation of Iran---and the broader struggle for human freedom---requires more than activists and organizers. It requires \textit{builders}: those who create the tools, tell the stories, and prove the theorems that make freedom possible.

\subsection{To the Artists}

Persian civilization has always been a civilization of artists. The miniaturists of Isfahan, the poets of Shiraz, the musicians of the classical radif, the filmmakers of the Iranian New Wave---art is how we remember who we are.

\textbf{We need you now.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Visual artists}: Create the imagery of freedom---posters, murals, digital art that inspires and unifies
    \item \textbf{Musicians}: Compose the anthems of liberation---songs that will be sung in the streets of Tehran
    \item \textbf{Writers}: Tell our stories---novels, poems, screenplays that capture the Persian spirit
    \item \textbf{Filmmakers}: Document the struggle---films that bear witness and move hearts
    \item \textbf{Designers}: Build the visual identity of a free Iran---logos, flags, symbols that unite
\end{itemize}

Art is not decoration. Art is \textit{infrastructure}. A movement without art is a movement without soul.

\subsection{To the Mathematicians}

Persian mathematics changed the world. Al-Khwarizmi gave us algebra. Omar Khayyam solved cubic equations. Nasir al-Din Tusi advanced trigonometry. This tradition of rigorous, beautiful mathematics is our heritage.

\textbf{We need your minds.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Cryptographers}: Design and analyze the protocols that protect activists
    \item \textbf{Game theorists}: Model the dynamics of regime collapse and peaceful transition
    \item \textbf{Mechanism designers}: Create voting systems, allocation mechanisms, governance structures that are manipulation-resistant
    \item \textbf{Statisticians}: Analyze human rights data, detect fraud, quantify suffering
    \item \textbf{Complexity theorists}: Prove the hardness assumptions that secure our communications
\end{itemize}

Every theorem you prove, every protocol you design, every attack you discover and fix---these are acts of liberation.

\subsection{To the Cryptographers}

You hold the keys to the kingdom---literally. The protocols you design determine whether activists can coordinate safely, whether journalists can protect sources, whether families can communicate without fear.

\textbf{We need your expertise.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Protocol designers}: Help us build and audit secure communication systems
    \item \textbf{Implementation experts}: Write secure code that withstands real-world attacks
    \item \textbf{Cryptanalysts}: Find vulnerabilities before adversaries do
    \item \textbf{Applied researchers}: Bridge the gap between academic advances and deployed systems
    \item \textbf{Educators}: Teach operational security to activists, journalists, citizens
\end{itemize}

The work you do in your lab, your office, your late-night coding sessions---this work protects lives. This work enables freedom.

\subsection{To the Engineers and Builders}

Software engineers, hardware designers, network architects, systems administrators---you build the infrastructure of the digital world.

\textbf{Build it for freedom.}

\begin{itemize}[leftmargin=*]
    \item \textbf{Contribute to open source}: Session, Signal, Tor, Matrix---these projects need developers
    \item \textbf{Build censorship-circumvention tools}: VPNs, proxies, mesh networks that work inside Iran
    \item \textbf{Design resilient systems}: Decentralized, fault-tolerant, surveillance-resistant
    \item \textbf{Audit and harden}: Find and fix vulnerabilities in freedom tools
    \item \textbf{Document and educate}: Write guides that help non-technical users protect themselves
\end{itemize}

\subsection{The CYRUS Grants for Builders}

The CYRUS DAO will establish grant programs specifically for artists, mathematicians, and engineers working on freedom tools:

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Grant Category} & \textbf{Focus} & \textbf{Examples} \\ \midrule
Art for Freedom & Visual, musical, literary works & Albums, films, murals \\
Cryptographic Research & Protocol design, analysis & New schemes, audits \\
Tool Development & Software for activists & Apps, libraries, guides \\
Education & Training materials & Courses, workshops, docs \\
Documentation & Human rights records & Archives, databases \\
\bottomrule
\end{tabular}
\caption{CYRUS Builder Grants}
\end{table}
