\section{News, Updates, and the Living Document}

\begin{center}
\textit{``Yesterday I was clever, so I wanted to change the world.\\
Today I am wise, so I am changing myself.''}\\
\vspace{0.2cm}
--- Rumi
\end{center}

\vspace{0.5cm}

A liberation movement must be adaptive. Conditions change. New challenges emerge. Opportunities arise. The CYRUS ecosystem includes infrastructure for ongoing communication and coordination.

\subsection{Official Channels}

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Channel} & \textbf{Purpose} & \textbf{Update Frequency} \\ \midrule
cyrus.cash & Official website, whitepaper & As needed \\
Twitter/X (@cyrus\_cash) & News, announcements & Daily \\
Telegram (CyrusCommunity) & Community discussion & Real-time \\
Discord & Technical discussion, governance & Real-time \\
GitHub (cyrusdao) & Code, proposals, documentation & Continuous \\
On-chain (Base) & Treasury, governance votes & Per transaction \\
\bottomrule
\end{tabular}
\caption{Official Communication Channels}
\end{table}

\subsection{Governance Proposals as News}

Every DAO proposal is a form of news---a signal of community priorities, a record of decisions, a log of action. The on-chain governance system creates an immutable, transparent record of:

\begin{itemize}[leftmargin=*]
    \item Grant recipients and amounts
    \item Treasury allocations
    \item Constitutional amendments
    \item Community resolutions
\end{itemize}

\subsection{The Whitepaper as Living Document}

This whitepaper is versioned and will be updated as the project evolves. Significant changes require DAO governance approval. The GitHub repository maintains full history:

\begin{center}
\url{https://github.com/cyrusdao/whitepaper}
\end{center}

\textbf{Current Version}: 1.4.0\\
\textbf{Last Updated}: \today

\newpage
