\section*{DISCLAIMER}
\addcontentsline{toc}{section}{Disclaimer}

\begin{tcolorbox}[colback=persianblue!10!white,colframe=persianblue,width=\textwidth,arc=3mm,boxrule=2pt]

\textbf{\Large THIS IS A COMMUNITY TOKEN}

\vspace{0.3cm}

\textbf{No Financial Advice}: Nothing in this whitepaper constitutes financial, investment, legal, or tax advice. Consult qualified professionals before making any financial decisions.

\vspace{0.2cm}

\textbf{No Expectation of Profit}: CYRUS is a community token honoring Persian heritage and the principles of Cyrus the Great. There is \textbf{NO expectation} of financial gain, profit, or returns of any kind. Token value may go to zero.

\vspace{0.2cm}

\textbf{Assume Total Loss}: Assume any funds used to acquire CYRUS may be lost entirely. Only participate with funds you can afford to lose completely.

\vspace{0.2cm}

\textbf{Community Initiative}: This project is a community initiative created by members of the Persian diaspora. It has no official affiliation with any government, museum, institution, or official entity.

\vspace{0.2cm}

\textbf{Historical Content}: While we strive for historical accuracy, this document is not an academic publication. Consult scholarly sources for detailed historical research.

\vspace{0.2cm}

\textbf{Not a Security}: CYRUS is not a security, investment contract, or financial instrument. It is a community token representing shared cultural values and enabling DAO governance.

\vspace{0.2cm}

\textbf{Regulatory Compliance}: Purchasers are responsible for compliance with local laws and regulations. CYRUS may not be available in all jurisdictions.

\vspace{0.3cm}

\textbf{By acquiring CYRUS tokens, you acknowledge and accept all risks and disclaimers described in this whitepaper.}

\end{tcolorbox}

\vspace{1cm}

\begin{center}
\rule{0.5\textwidth}{0.4pt}

\vspace{0.5cm}

\textbf{Join the PARS Community:}

\vspace{0.3cm}

Website: \url{https://cyrus.cash}

Twitter/X: @cyrus\_cash

Telegram: @CyrusCommunity

Discord: \url{https://discord.gg/cyrus}

GitHub: \url{https://github.com/luxdao/cyrus}

\vspace{0.5cm}

\textit{Honoring the Father of Human Rights}

\vspace{0.2cm}

\textit{Uniting the Persian Diaspora}

\vspace{0.3cm}

{\small Cyrus the Great (Kourosh-e Bozorg) | c. 600--530 BCE}

{\small Founder of the Achaemenid Empire | Author of the Cyrus Cylinder}

\vspace{0.3cm}

{\color{persiangold}$\bigstar$} \textsc{Az M\=a Beh M\=a --- From Us, For Us} {\color{persiangold}$\bigstar$}

\end{center}
